Lossy compression of DNA sequencing quality data

### 2015-02-06 manuscript/q-compression.tex
Added additional species info to text.

\textit{Rhodobacter sphaeroides} 2.4.1 data from the \textsc{gage}
(Genome Assembly Gold-Standard Evaluations)~\cite{Salzberg:2012rc},
which are generated from a fragment library (insert size of 180 nt;
2,050,868 paired-end reads) and short-jump library (insert size of
3,000 nt; 2,050,868 reads). The corresponding reference sequence was
obtained from the NCBI RefSeq database (NC\_007488.1, NC\_007489.1,
NC\_007490.1, NC\_007493.1, NC\_007494.1, NC\_009007.1, NC\_009008.1).

\textit{Homo sapiens} \ldots

\textit{Genus speices} \ldots

>>>>

\textit{Rhodobacter sphaeroides} 2.4.1 data from the \textsc{gage}
(Genome Assembly Gold-Standard Evaluations)~\cite{Salzberg:2012rc},
which are generated from a fragment library (insert size of 180 nt;
2,050,868 paired-end reads) and short-jump library (insert size of
3,500 nt; 2,050,868 reads). The corresponding reference sequence was
obtained from the NCBI RefSeq database (NC\_007488.1, NC\_007489.1,
NC\_007490.1, NC\_007493.1, NC\_007494.1, NC\_009007.1, NC\_009008.1).

\textit{Stapylococcus aureus} USA300 data from the \textsc{gage}~\cite{Salzberg:2012rc}, which are generated from a fragment library (insert size of 180 nt; 1,294,104 paired-end reads) and short-jump library (insert size of 3,500 nt; 3,494,070 reads).
The corresponding reference sequence was obtained from the NCBI RefSeq database (NC\_010063.1, NC\_010079.1, NC\_012417.1).

\textit{Homo sapiens} chromosome 14 data from the \textsc{gage}~\cite{Salzberg:2012rc}, which are generated from a fragment library (insert size of 155 nt; 36,504,800 paired-end reads) and short-jump library (insert sizes ranging from  2283-2803 nt; 22,669,408 reads).
The corresponding reference sequence was obtained from the NCBI RefSeq database (NC\_000014.8).

\textit{TODO: MiSeq data set} \ldots
